### 2014-09-03 tex/definitions.tex
Miscellaneous fixes and improvements to all proofs
Added preliminary definition for initial states

\begin{definition}
\label{def:initate}
The set of \textbf{initial states} $\mathcal{S}_0$ is defined as (TBD)
\end{definition}

@@

\begin{definition}
For a given function $f:A \mapsto B$, the \textbf{image} $f^\rightarrow$ and \textbf{preimage} $f^\leftarrow$ are defined as
\begin{align}
 f^\rightarrow &= \{ f(a) \mid a \in A\}\\
 f^\leftarrow &= \{ a \mid f(a) \in B \}§
 \end{align}
\end{definition}

>>>>

\begin{definition}
\label{def:initstate}
$\mathcal{S}_0$ is defined as the set of \textbf{initial states}. An initial state is a state meeting the following conditions:  The range of L has exactly three locations: $l_{null}$, $l_{un}$, and $l_0$, the function R is defined only for location $l_0$, and for any field $f$, $R(l_0,f)$ returns $r_{un}$. 
\end{definition}

@@

\begin{definition}
For a given function $f:A \mapsto B$, the \textbf{image} $f^\rightarrow$ and \textbf{preimage} $f^\leftarrow$ are defined as
\begin{align}
 f^\rightarrow &= \{ f(a) \mid a \in A\}\\
 f^\leftarrow &= \{ a \mid f(a) \in B \}
 \end{align}
 The bracket notation $ f^\rightarrow [C] $ is used to denote that the image is drawn from a specific subset:
 \begin{align}
 f^\rightarrow [C] &= \{ f(a) \mid a \in C\}\\
 f^\leftarrow [D] &= \{ a \mid f(a) \in D \}
 \end{align}
 Where $C \subset A$ and $D \subset B$
\end{definition}
